Constructing Quotient Inductive-Inductive Types

### 2018-10-20 paper.tex
add authors, remove blindness

\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

%% Author with single affiliation.
\author{First1 Last1}
\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position1}
  \department{Department1}              %% \department is recommended
  \institution{Institution1}            %% \institution is required
  \streetaddress{Street1 Address1}
  \city{City1}
  \state{State1}
  \postcode{Post-Code1}
  \country{Country1}                    %% \country is recommended
}
\email{first1.last1@inst1.edu}          %% \email is recommended

%% Author with two affiliations and emails.
\author{First2 Last2}
\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
  \position{Position2a}
  \department{Department2a}             %% \department is recommended
  \institution{Institution2a}           %% \institution is required
  \streetaddress{Street2a Address2a}
  \city{City2a}
  \state{State2a}
  \postcode{Post-Code2a}
  \country{Country2a}                   %% \country is recommended
}
\email{first2.last2@inst2a.com}         %% \email is recommended
\affiliation{
  \position{Position2b}
  \department{Department2b}             %% \department is recommended
  \institution{Institution2b}           %% \institution is required
  \streetaddress{Street3b Address2b}
  \city{City2b}
  \state{State2b}
  \postcode{Post-Code2b}
  \country{Country2b}                   %% \country is recommended
}
\email{first2.last2@inst2b.org}         %% \email is recommended

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
This work was supported by the European Union, co-financed by the
European Social Fund (EFOP-3.6.3-VEKOP-16-2017-00002) and COST Action
EUTypes CA15123, and by the National Research, Development and
Innovation Office -- NKFIH project 127740.
\end{acks}

>>>>

\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

%% Author with single affiliation.
\author{Thorsten Altenkirch}
%\authornote{with author1 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
%  \position{Position1}
  \department{School of Computer Science}              %% \department is recommended
  \institution{University of Nottingham}            %% \institution is required
%  \streetaddress{Street1 Address1}
%  \city{City1}
%  \state{State1}
%  \postcode{Post-Code1}
  \country{United Kingdom}                    %% \country is recommended
}
\email{Thorsten.Altenkirch@nottingham.ac.uk}          %% \email is recommended

%% Author with two affiliations and emails.
\author{Ambrus Kaposi}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0001-9897-8936}             %% \orcid is optional
\affiliation{
  %\position{Position2a}
  \department{Department of Programming Languages and Compilers}             %% \department is recommended
  \institution{E{\"o}tv{\"o}s Lor{\'a}nd University}           %% \institution is required
%  \streetaddress{Street2a Address2a}
  \city{Budapest}
%  \state{State2a}
%  \postcode{Post-Code2a}
  \country{Hungary}                   %% \country is recommended
}
\email{akaposi@inf.elte.hu}         %% \email is recommended

\author{Andr{\'a}s Kov{\'a}cs}
%\authornote{with author2 note}          %% \authornote is optional;
                                        %% can be repeated if necessary
\orcid{0000-0002-6375-9781}             %% \orcid is optional
\affiliation{
  %\position{Position2a}
  \department{Department of Programming Languages and Compilers}             %% \department is recommended
  \institution{E{\"o}tv{\"o}s Lor{\'a}nd University}           %% \institution is required
%  \streetaddress{Street2a Address2a}
  \city{Budapest}
%  \state{State2a}
%  \postcode{Post-Code2a}
  \country{Hungary}                   %% \country is recommended
}
\email{kovacsandras@inf.elte.hu}         %% \email is recommended

@@

%% Acknowledgments
\begin{acks}                            %% acks environment is optional
This work was supported by the European Union, co-financed by the
European Social Fund (EFOP-3.6.3-VEKOP-16-2017-00002) and COST Action
EUTypes CA15123.
\end{acks}
